### 2017-07-28 README.Rmd
added acknowledgement of Noam Ross, Sean Huges, and Mara Averick (https://github.com/ropensci/onboarding/issues/87)

Thanks also to Carson Sievert for writing the code that combined `plotly` with `visdat`, and for Noam Ross for suggesting this in the first place.

>>>>

Thanks to Carson Sievert for writing the code that combined `plotly` with `visdat`, and for Noam Ross for suggesting this in the first place.

Finally thank you to [rOpenSci](https://github.com/ropensci) and it's amazing [onboarding process](https://github.com/ropensci/onboarding), this process has made visdat a much better package, thanks to the editor Noam Ross (@noamross), and the reviewers Sean Hughes (@seaaan) and Mara Averick (@batpigandme).
